---
title: "WeightMatters"
author: "Krupa R"

output: html_document
hitheme: tomorrow

knit: slidify::knit2slides
mode: selfcontained
highlighter: prettify
subtitle: Predicting Weight based on Height using Women dataset
framework: io2012
---

### WeightMatters

#### Predicting Weight based on Height using Women dataset

---

### Overview

* This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

* The app developed for the first part of the assignment demo is avalilable at  https://krupar.shinyapps.io/HeightWeight/

* The Source code for ui.R and server.R files are available on GitHub at https://github.com/KrupaR/Developing-Data-Products

---

### Functionality of Application

* The application predicts average weight of American women who are in the age bracket of 30 to 39 years based on their height

* Uses __Women__ dataset of R for the prediction

* The user has to enter Height in Inches. Since the dataaset has entries for Height between 58 inches to 72 inches, a basic range verification id done in the program and appropriate error message is displayed

* The output (Weight) is displayed in Pounds as well as in Kilograms

---



### R Code used


The Dataset Women is used for this application

```{r echo=FALSE}
knitr::opts_chunk$set(opts.label="kill_prefix")
```

``` {r, comment= NA,result='asis'}
str(women)
head(women,4)
```

---

### Sample code

The function which fetches the Weight based on Height is as follows:
``` {r, comment=NA}
avgWeight <- function(height)
{
  for (i in 1: nrow(women))
  {
    if (women[i,1] == height )
    {
  return(women[i,2])
     }
  }
}

```



